\documentclass[a4paper,40pt]{article} % Reduced font size
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\geometry{margin=0.6in}
\setlength{\parindent}{0pt} % No indentation
\setlength{\parskip}{0em} % Minimal paragraph spacing

% Custom list spacing
\setlist[itemize]{itemsep=-0.3em, topsep=0.1em, leftmargin=1.5em} % Compact list spacing
\renewcommand{\baselinestretch}{0.89}
\pagenumbering{gobble}

% Custom section title with underline
\newcommand{\sectiontitle}[1]{%
    \vspace{1em} % Ensure consistent space above the title
    \textbf{\LARGE #1} % Bold section title
    \vspace{0.29em} % Space between title and line
    \hrule height 0.5pt % Horizontal line
    \vspace{0.41em} % Uniform space after the line before content
}

\begin{document}

% HEADER
\begin{center}
    {\LARGE \textbf{Zohair Omar}} \\
    \small \href{mailto:zohairomar@gmail.com}{zohairomar@gmail.com} | +1-604-8628753 |
    \href{https://linkedin.com/in/zohairomar}{linkedin.com/in/zohairomar} |
    \href{https://github.com/zohairomar1}{github.com/zohairomar1}

    \vspace{0.3em}


\end{center}

\vspace{-1.3em} % Reduced space after header

% TECHNICAL SKILLS
\sectiontitle{Technical Skills}
\textbf{Programming Languages:} Python, SQL, Java, JavaScript, C \\
\textbf{Web Development \& APIs:} React, Tailwind CSS, Flask, Streamlit, REST APIs, Postman, Docker, HTML/CSS \\
\textbf{Testing \& DevOps:} Unit Testing (JUnit5), CI/CD (GitHub Actions), Version Control (Git) \\
\textbf{Data Analysis \& Visualization:} Excel (Pivot Tables, VLOOKUP, Charts), Power BI, Pandas, NumPy, statsmodels, Matplotlib, Plotly \\
\textbf{Developer \& Office Tools:} VS Code, IntelliJ, PyCharm, Codenvy, Microsoft Word, PowerPoint, Power Automate

\vspace {-0.7em}

% EDUCATION
\sectiontitle{Education}
\textbf{Bachelor of Science, Computer Science \&\ Mathematics (Minor in Economics)} \hfill {Expected December 2026} \\
{University of Calgary, Alberta} \\

% \vspace{-0.7em}
% \textit{Transferred from University of British Columbia in Fall 2024} \\

% \vspace{0.2em}


\textbf{Bachelor of Science, Computer Science} \hfill {Sep 2022 - Sep 2024} \\
{University of British Columbia, Vancouver} \\

\vspace{-0.86em}

\textit{\textbf{Key Courses:}} Object-Oriented Programming, Data Structures \& Algorithms, Functional Programming, Applied Machine Learning (Python), Introduction to Data Science (R)

\vspace {-0.35em}

% EXPERIENCE
\sectiontitle{Experience}

\textbf{Enactus UCalgary - WealthPath} \hfill {Jul 2025 – Present} \\
Front-End Development Lead; React, TypeScript, Tailwind CSS \hfill \textit{Calgary, AB}
\begin{itemize}
    \item Lead a 4-person front-end team to develop a financial literacy platform for young adults; facilitate 2–3 Scrum meetings per week to align priorities and track deliverables.
    \item Built a reusable \textbf{React/TypeScript} component library adopted across 5+ core pages, reducing duplicate code by approximately 20\%.
    \item Coordinated with the back-end team to define API contracts and resolve integration issues, accelerating feature delivery by 1–2 sprints compared to earlier timelines.
    \item Implemented a \textbf{CI/CD pipeline} with GitHub Actions that now runs automated linting and tests on every pull request; supported over 30 successful merges without regression.
    \item Built and deployed the platform pilot through partnerships with 2–3 schools, impacting 100+ students in the first semester.
\end{itemize}


\textbf{\href{https://v0-tech-websitemain1-vu.vercel.app/}{TechNova}} \hfill {February 2025 – Present} \\
Co-Founder \& VP Technical; React, JavaScript, HTML/CSS, Python, SQL, Git \hfill \textit{Calgary, AB}
\begin{itemize}
    \item Built full-stack websites for clubs using React, Python \&\ SQL, focusing on modular design and maintainability.
    \item Led a team of 4 developers through Agile sprints, leveraging Git and code reviews for clean, testable code.
    \item Implemented user login, responsive UIs, and dashboards to improve functionality \&\ user experience for 100+ users.
    \item Created documentation and onboarding guides to support faster ramp-up and long-term technical system upkeep.
\end{itemize}



\vspace{0.2em} % Adjusted spacing between jobs

\textbf{Agrius IT} \hfill {May 2024 - July 2024} \\
Software Developer Intern; Python, SQL, HTML/CSS, JavaScript \hfill \textit {Abu Dhabi, UAE}
\begin{itemize}
    \item Fortified web application security by integrating enterprise-grade security protocols, including CORS, proxy settings, and error handling protocols; directly mitigated risk of cyberattacks while ensuring uninterrupted service for 1,000+ daily users accessing the platform.
    \item Documented workflows and contributed to internal SOPs for issue resolution and system operations using Word.
    \item Facilitated cross-functional collaboration to troubleshoot and deliver feature updates, resolving three critical system bottlenecks and meeting all deadlines ahead of schedule.
    \item Developed and debugged secure backend solutions involving user authentication and role-based access control using SQL, improving database query performance and security.
\end{itemize}

\textbf{UBC Design League} \hfill {Dec 2022 -- Sept 2024} \\
Software Developer; Python, C, SolidWorks, Arduino IDE, Git \hfill \textit{Vancouver, BC}

\begin{itemize}
    \item Directed software design and system integration for a competition-ready autonomous robot with object detection, applying advanced Programming Language Theory for seamless integration.
    \item Programmed in Arduino IDE using C to develop algorithms for object detection, path planning, and robot control, achieving a 95\% success rate in tests.
    \item Mastered SolidWorks for advanced 3D modeling and prototyping, enhancing design visualization and prototype development for an autonomous robot project.
    \item Integrated and programmed servo motors and ultrasonic sensors for obstacle detection and avoidance, increasing real-time perception efficiency by 25\%.
\end{itemize}



\vspace {-0.78em}

% PROJECTS
\sectiontitle{Projects}
\textbf{UBC Thrifty Grocers}; Go, Postman, React, JavaScript, Tailwind CSS
\begin{itemize}
    \item Engineered high-performance back-end services for a grocery delivery platform using Go, leading to a 40\%\ increase in server response speed, while quickly  learning the language to contribute effectively to project success.
    \item Conducted extensive API testing using Postman and Bash Scripts, achieving a 100\% success rate in test cases, ensuring flawless functionality and reliability of the web application.
    \item Applied security measures (CORS \&\ proxies) and implemented access control logic in backend services to ensure users accessed only authorized resources, resulting in a 99\%\ error-free deployment rate.
    \item Utilized React to create responsive webpages using Tailwind CSS for 50+ users to easily deliver groceries.
\end{itemize}

\href{https://github.com/zohairomar1/oil-and-gas-dashboard}{\textbf{Oil \& Gas Asset Integrity Dashboard}}; Power BI, SQL Server, SharePoint
\begin{itemize}
  \item Built a production-like \textbf{Power BI} solution to monitor integrity KPIs for natural-gas assets: corrosion rate (mmpy), oil content (ppm), SRB levels, overdue inspections, anomaly tracking, certification compliance.
  \item Modeled \textbf{24 months} of data with Power Query + DAX; implemented role-based views for engineers vs. managers, slicers by department/month/year, and refresh simulation.
  \item Enabled proactive planning with backlog alerts and compliance trend summaries for stakeholder reports.
\end{itemize}

\vspace{0.15em} % Adjusted spacing between projects

\href{https://github.com/zohairomar1/ComfortCorner}{\textbf{nwHacks 2024: Comfort Corner}}; JavaScript, HTML/CSS
\begin{itemize}
    \item Led the development of a mental health support website at Western Canada's largest hackathon nwHacks 2024, achieving a top 10 placement with 653 participants.
    \item Successfully integrated OpenAI API to power a specialized chatbot created for mental health assistance, leveraging advanced natural language processing techniques to provide empathetic and accurate support.
    \item Designed and implemented a user-friendly interface featuring quotes and resources, enhancing visitor engagement.
\end{itemize}

\vspace{0.1em} % Adjusted spacing between projects


\href{https://github.com/zohairomar1/BusinessTrackingApp}{\textbf{Business Tracking Application}}; Java, JUnit, JSON, UML
\begin{itemize}
    \item Developed a Java-based application using OOP principles and software development practices to help businesses track purchases and analyze revenue data.
    \item Built an interactive GUI with Java Swing for adding, filtering, and visualizing purchases; implemented unit tests with JUnit to ensure system reliability.
\end{itemize}

\href{https://github.com/zohairomar1/HeartDiseasePredictionModel}{\textbf{Heart Disease Prediction Model}}; R, tidyverse, Jupyter
\begin{itemize}
    \item Built predictive ML model to classify heart disease likelihood based on 300+ patient records.
    \item Applied KNN algorithm after performing data cleaning, feature scaling, and statistical analysis.
    \item Achieved 83\% model accuracy and visualized feature impact; emphasized predictive modeling and business insight.
\end{itemize}

\href{https://wilf-life-climate-change-crisis.vercel.app/}
{\textbf{CalgaryHacks 2025: WildBC}}; TypeScript, Next.js, React
\begin{itemize}
    \item Co-developed a web application in a 24-hour hackathon to raise awareness of wildlife conservation in British Columbia in the context of climate change.
    \item Built an interactive map visualizing endangered species and wildfire locations with clickable insights to support public education and engagement.
    \item Implemented a timeline feature to track wildfire events over time, including incidents through 2025.
    \item Created an educational hub with videos, articles, quizzes, and leaderboards to encourage learning through interactive content.
    \item Designed a discussion board to support expert Q\&A and community conversations, and integrated event listings for conservation workshops and outreach.
\end{itemize}

\href{https://github.com/zohairomar1/volve-production-forecast}{\textbf{Production Analytics \& Forecasting Dashboard}}; Python, Streamlit, statsmodels, Plotly, Power Automate
\begin{itemize}
    \item Built an interactive analytics dashboard to explore and validate time-series operational data (2008--2016), improving stakeholder visibility into trends and exceptions.
    \item Developed rolling-origin backtesting to benchmark ETS forecasts vs.\ a seasonal naive baseline, achieving 45\% lower MAE and 46\% lower RMSE on the default evaluation view.
    \item Supported testing and defect-style validation by implementing a metrics pipeline (MAE, RMSE, MAPE, WAPE) with near-zero handling for stability and clearer interpretation.
    \item Implemented a \textbf{Power Automate} workflow that ingests exported forecast/anomaly CSVs, generates a summary email from templates, and distributes results via \textbf{Outlook} on a scheduled or event-based trigger.
\end{itemize}


\end{document}
